
```{r setup, include=FALSE}
# Pre-load libraries

knitr::opts_chunk$set(echo = TRUE)
library(fBasics)
library(fpp2)
library(tidyverse)
library(lubridate)
library(prophet)
library(forecast)
library(fBasics)
library(ggplot2)


library(magrittr)
library(dplyr)
library(tidyverse)
library(caTools)

library(nbastatR)

library(caret)
library(MASS)
library(reshape2)
library(cluster)

library(factoextra)

library(ggfortify)

library(rlist)

library(hrbrthemes)

library(data.table)
#options(digits=4)
```





**2. Looking at page 255 (Figure 28.4) in Mathletics, conduct a similar analysis that determines the relative importance of each of the four factors. Based on your findings, how many games should we have won last year?**

Let's read in general Lakers team stats from the 2021-22 and 2-22-23 seasons.

```{r}
lakers_ff <- read.csv(file = 'lakers_four_factors.csv')

colnames(lakers_ff)
```

```{r}
EFG <- (lakers_ff$FG + (0.5 * lakers_ff$X3P))/lakers_ff$FGA
OppEFG <- (lakers_ff$OppFG + (0.5 * lakers_ff$Opp3P))/lakers_ff$OppFGA
DiffEFG <- EFG - OppEFG

TPP <- lakers_ff$TOV / (lakers_ff$FGA + (0.44 * lakers_ff$FTA) + lakers_ff$TOV)
OppTPP <- lakers_ff$OppTOV / (lakers_ff$OppFGA + (0.44 * lakers_ff$OppFTA) + lakers_ff$OppTOV)
DiffTPP <- TPP - OppTPP

ORP <- lakers_ff$ORB / (lakers_ff$ORB + lakers_ff$OppDRB)
DRP <- lakers_ff$DRB / (lakers_ff$OppORB + lakers_ff$DRB)
DiffRP <- ORP - DRP

FTR <- lakers_ff$FT / lakers_ff$FGA
OppFTR <- lakers_ff$OppFT/lakers_ff$OppFGA
DiffFTR <- FTR - OppFTR

games_won <- 59.05 + (383.31*(DiffEFG)) - (244.36*(DiffTPP)) + (34.49*(DiffRP)) + (84.27*(DiffFTR))
games_won
```


Based on the Mathletics formula and using the Four Factors, the Los Angeles Lakers were projected to win 37 games in 2021-22 (record was 33-49), and are projected to win 42 games this season (they are currently 32-34 as of this morning on March 10,2023).



-------------- Building our own model: -----------------


```{r}
four_factors_2021_22_df <- read.csv(file = 'four_factors_2021_22.csv')
model_four_factors_2021_22 <- lm(W ~ DIFF_EFG_PCT + DIFF_TOV_PCT + DIFF_REB_PCT + DIFF_FTA_RATE, 
                                 data=four_factors_2021_22_df)
summary(model_four_factors_2021_22)
```

Predict Lakers 2021-22 win record

```{r}
lakers_ff_2021_22_df <- four_factors_2021_22_df[four_factors_2021_22_df$TEAM_ID == 1610612747,]
predictions <- predict(model_four_factors_2021_22, newdata=lakers_ff_2021_22_df)
predictions
```

Based on the 2021-22 NBA season Four Factors data and model, the Los Angeles Lakers were projected to win 32 games in 2021-22, winning one more game than predicted (record was 33-49).



















